OneD: increasing reproducibility of Hi-C Samples with abnormal karyotypes

### 2018-01-04 manuscript_nar.tex
first changes for R2

Our approach is to model the total number of contacts for each bin, thus
reducing the matrix to a one-dimension score (hence the name
\textit{OneD}) referred to as the `contact profile'. We assume that the
total number of contacts per bin $t_{i}$ can be approximated by a
negative binomial distribution. This choice is sensible because the amount
of contacts is a discrete variable and because the negative binomial
distribution allows for overdispersion. We further assume that the
explicit sources of bias have independent contributions to the mean of the
distribution for a given bin $\lambda_i$.

@@

We developed the routines contained in the \texttt{dryhic} R package
(available at http://www.github.com/qenvio/dryhic) to efficiently create
sparse representations of contact matrices and further apply
\textit{vanilla}, \textit{ICE}, \textit{KR} and \textit{oneD} corrections.
\texttt{HiTC} \citep{servant2012hitc} and \texttt{HiCapp}
\citep{wu2016computational} were used to carry out the \textit{LGF} and
\textit{caICB} corrections respectively. When not specified, the
resolution of the analysis is 100~Kbp.

>>>>

Our approach is to model the total number of contacts for each bin, thus
reducing the matrix to a one-dimension score (hence the name
\textit{OneD}) referred to as the `contact profile'. We assume that the
total number of contacts per bin $t_{i}$ can be approximated by a
negative binomial distribution. This choice is sensible because the amount
of contacts is a discrete variable that often presents a variance higher
than the mean \citep{carty2017integrated} (a phenomenon known as
overdispersion), and because the negative binomial distribution allows
for overdispersion \citep{love2014moderated}. We further assume that
the explicit sources of bias have independent contributions to the mean
of the distribution for a given bin $\lambda_i$.

@@

We developed the routines contained in the \texttt{dryhic} R package
(available at http://www.github.com/qenvio/dryhic) to efficiently create
sparse representations of contact matrices and further apply
\textit{vanilla} (a single iteration of ICE), \textit{ICE}, \textit{KR} and \textit{oneD} corrections.
\texttt{HiTC} \citep{servant2012hitc} and \texttt{HiCapp}
\citep{wu2016computational} were used to carry out the \textit{LGF} and
\textit{caICB} corrections respectively. When not specified, the
resolution of the analysis is 100~Kbp.
